---
title: "simulation1 for mvHTP"
author: "xuziya"
date: "2022/4/14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load functions

```{r }
source('E:/rmu_study/project/mvHTP/generatedata.R')
source('E:/rmu_study/project/mvHTP/HTP.R')
source('E:/rmu_study/project/mvHTP/mvHTP.R')

```





## basic setting
```{r }
q=2
pz=40;px=0
p=px+pz
beta=c(1,1)
gamma=matrix(rnorm(pz*q),pz,q)

rho=0.5
pi=rep(0,pz);pi[1:5]=rho #sbar=5

```

###test part

A simple test to check whether HTP can recover the support. We may need a cross-validation function to choose s, but treat s as tuning parameter at present
```{r}
intercept=FALSE

s=16 #to satisfy sbar+2s<p,q+2s<p and s>(2+M/m)sbar, need 15<s<18
tuning=30
Gamma = gamma%*%beta +pi

HTP(Gamma,gamma,s)
HTP(Gamma,gamma,17) #successfully recover

# more large s to show the condition is not sharp
HTP(Gamma,gamma,18) #successfully recover 
HTP(Gamma,gamma,20) #successfully recover 
HTP(Gamma,gamma,22) #successfully recover

```
```{r}
r=1
n=400 # n>> plogq(p+2s) at least>p^(3/2)=354
data=generatedata(n,r,beta,gamma,pi)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=17,intercept=intercept,tuning = tuning,V=data$V,S=data$S)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=20,intercept=intercept,tuning = tuning,V=data$V,S=data$S)

n=600
data=generatedata(n,r,beta,gamma,pi)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=17,intercept=intercept,tuning = tuning,V=data$V,S=data$S)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=20,intercept=intercept,tuning = tuning,V=data$V,S=data$S)

n=800
data=generatedata(n,r,beta,gamma,pi)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=17,intercept=intercept,tuning = tuning,V=data$V,S=data$S)
mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=20,intercept=intercept,tuning = tuning,V=data$V,S=data$S)

```
Note at this time $s>3\bar{s}$ and $2s+\bar{s}\leq p$, then at most 1/7 IVs are invalid, which actually doesn't have much influence. But we should notice that the condition is not neccessary.


this is runaverage function for R times in tn sample size
```{r,echo=FALSE}

runaverage <- function(R,tn,beta,gamma,pi,s,OutputRes=FALSE,intercept=FALSE,tuning=30){
  #tmethod = c("oracle","naive 2SLS","OLS","mvHTP") # may add Jack method like egger regressioin
  TP=FP=array(dim = c(length(tn),R))
  error=coverage=len=array(dim = c(length(tn),q,R))
  
  for (k in 1:length(tn)) {
    n=tn[k]
    for (r in 1:R) {
      data=generatedata(n,r,beta,gamma,pi)
          res=mvHTP(Y=data$Y,D=data$D,Z=data$Z,X=data$X,s=s,intercept=intercept,tuning = tuning,OutputRes=OutputRes,V=data$V,S=data$S)
        Vhat=as.vector(res$Vhat)
        TP[k,r]=length(intersect(data$V,res$Vhat))
        FP[k,r]=length(res$Vhat)-TP[k,r ]
        #FN[r ]=length(V)-TP[r ]
        #TN[r ]=length(Shat)-length(Vhat)-FN[r ]
        error[k,,r]=(beta-res$betahat)
        coverage[k,,r]=((beta<=(res$ci)[,2])+(beta>=(res$ci)[,1])==2)
        len[k,,r ]=(res$ci)[,2]-(res$ci)[,1]
    }
    }
  return(list(TP=TP,FP=FP,error=error,coverage=coverage,len=len))
}



```

```{r}
R=500;tn=c(400,600,800);s=20
list=runaverage(R,tn,beta,gamma,pi,s,intercept=FALSE,tuning=30)
apply(abs(list$error), c(1,2), mean)
hist(list$error[1,2,])
apply(list$coverage, c(1,2), mean)
apply((list$TP/(list$TP+list$FP)),1,mean)
apply(list$FP,1,mean)
```
